---
title: "\U0001D67F\U0001D670\U0001D7F7_\U0001D69D\U0001D68E\U0001D696\U0001D699\U0001D695\U0001D68A\U0001D69D\U0001D68E"
author: "Ahmed Mohy"
date: "September 18, 2016"
output: 
  html_document: 
    keep_md: yes
---


Load the Data



```{r load,echo=TRUE}
activity =  read.csv("/Users/AMOHY/activity.csv")

```

Calculate the total number of steps per day

```{r total number, echo=TRUE}
library(dplyr)
library(ggplot2)
histogram1 <- activity %>% group_by(date)  %>% summarise(steps = sum(steps,na.rm=TRUE))
qplot(date,steps,data=activity,geom ="line")
```

Calculate and report the mean and median of the total number of steps taken per day

```{r mean, echo=TRUE}
Mean = mean(activity$steps,na.rm=TRUE)
Median = median(activity$steps,na.rm=TRUE)
```

Which 5-minute interval contains the maximum average number of steps

```{r Time series, echo=TRUE}
Summary1 <- activity %>% group_by(interval)  %>% summarise(steps = mean(steps,na.rm=TRUE))
plot(Summary1$interval,Summary1$steps,type="l")
max_interval = Summary1[which(Summary1$steps==max(Summary1$steps)),1]
```

report the total number of missing values in the dataset

```{r missing, echo=TRUE}
missing_values = length(which(is.na(activity$steps)==1))
```

strategy for filling in all of the missing values in the dataset

```{r strategy, echo=TRUE}
new_activity <- inner_join(activity,Summary1, by = "interval")
new_activity$steps.x[which(is.na(new_activity$steps.x)==1)]=new_activity$steps.y[which(is.na(new_activity$steps.x)==1)]
new_activity=new_activity[,1:3]
names(new_activity)=c("steps","date","interval")
```

Calculate the total number of steps taken per day after imputing missing values

```{r total number 2, echo=TRUE}
histogram2<- new_activity %>% group_by(date)  %>% summarise(steps = sum(steps))
qplot(date,steps,data=new_activity,geom ="line")
```

Calculate and report the mean and median of the total number of steps taken per day after imputing missing values

```{r mean_1, echo=TRUE}
Mean_1 = mean(new_activity$steps)
Median_1 = median(new_activity$steps)
```

differences in activity patterns between weekdays and weekends

```{r weekday Vs. weekend}
new_activity <- cbind(new_activity,weekdays(as.Date(new_activity$date)))
Weekday <- replicate(length(new_activity$steps),"weekday")
new_activity <- cbind(new_activity,Weekday)
DayType <- factor(c("weekday","weekend"))
names(new_activity)<-c("steps","date","interval","Day","DayType")
new_activity$Day <- as.character(new_activity$Day)
new_activity$DayType <- as.character(new_activity$DayType)
new_activity$DayType[which(new_activity$Day=="Saturday" | new_activity$Day=="Sunday")]  ="weekend"
Summary4<- new_activity %>% group_by(interval,DayType)  %>% summarise(steps = mean(steps))
qplot(interval,steps,data=Summary4,facets=DayType~.,geom=c("line"))
```